---
title: "Machine Learning"
author: "Jonah Winninghoff"
date: "1/4/2020"
output: ioslides_presentation
---

##
#### How can the Machine Prediction possibly predict such a complex graph? The machine learning can only see 60% of dataset!
```{r echo=FALSE, eval=TRUE, message=FALSE}
library(plotly)
library(caret)
library(ElemStatLearn)
library(dplyr)
library(ggplot2)
library(gbm)
library(e1071)

data(CO2)
    set.seed(345)
    inTrain <- createDataPartition(CO2$Treatment,p=.6,list=F)
    training <- CO2[inTrain,]
    testing <- CO2[-inTrain,]
    modFit <- train(Treatment ~ ., method="gbm",data=training,verbose=FALSE)
 
plot_ly(training,x=~uptake,y=~conc,color=~Treatment, type="scatter", mode = "markers",size=2,
        colors = c("rosybrown","coral"))%>%
        layout(xaxis = list(title="uptake rates (umol/m^2 sec)"),yaxis=list(title = "CO2 concentrations (mL/L)"))
```


##
##### Then, it makes a prediction of what 40% of other dataset looks like!
```{r echo=FALSE, eval=TRUE, message=FALSE}
plot_ly(testing,x=~uptake,y=~conc,color=~Treatment,
        type="scatter",size=2,colors = c("rosybrown","coral"))%>%
        layout(xaxis = list(title="uptake rates (umol/m^2 sec)"),
        yaxis=list(title = "CO2 concentrations (mL/L)"))
```

## Did it get wrong? Sometimes. But at this time, it does not get wrong!
#### Here's proof

```{r echo=TRUE,eval=TRUE,message=TRUE}
P<-confusionMatrix(testing$Treatment,predict(modFit,testing))
P$table
P$overall[1]
```

##
#### Do you want to see how this prediction can happen?
```{r echo=TRUE}
data(CO2)
    set.seed(345)
    inTrain <- createDataPartition(CO2$Treatment,p=.6,list=F)
    training <- CO2[inTrain,]
    testing <- CO2[-inTrain,]
    modFit <- train(Treatment~.,
      method="gbm",data=training,verbose=FALSE)
predict(modFit, testing)
```

##
#### There are many basic machine learning tools that can be used.
For example:

- Boosting (gbm)
- Simple linear regression (lm)
- Random Forest (rf)
- RPart (rpart)


But how do I know which the one is right to use for prediction?

# This is what Data Science Specialization certification is for!
